Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2020-12-20 GWLDCII.tex
going back through the referee reports, two pages left of report M

This paper is the second in a two part series investigating the combinatorics and geometry underlying Wilson loop diagrams in SYM $N=4$ theory. This series lays out several results about the relationship between Wilson loop diagrams and the positroid cells that give a CW complex structure to the positive Grassmanian. This paper is concerned with identifying which positroid cells correspond to which Wilson loop diagrams, and how this translates to a geometric tiling of a subspace of the positive Grassmannians.

@@

It is worth noting at this point that the \hlfix{combinatorics of the Wilson loop diagrams are different from the combinatorics of the Amplituhedron}{I think we should discuss this paragraph -- it may be misleading in a bad way}, just as the the volume forms associated to the BCFW diagrams are different from those associated to the Wilson Loop diagrams. For instance, the BCFW are most readily related to the geometry of a postive Grassmanian via plabic graphs. Meanwhile, the Wilson loop diagrams correspond to matrices with variable valued entries (see section \ref{section WLD background}) and Grassmann Necklaces (see Algorithm \ref{alg:put GN on WLD}).  These two combinatorial representations of the positive Grassmannians have different strengths and weaknesses, and it is not possible to give a one to one translation of the combinatorial tools used for the Amplituhedron and BCFW diagrams, and the combinatorial tools used for the Wilson loop diagrams, associated matrices and Grassmann Necklaces. For instance, square moves and merge-expand moves give different graphical representations of the same positroid cell. There is no equivalent diagramatical equivalence for Wilson loop diagrams, though it has been shown (see \cite{wilsonloop, generalcombinatoricsI}) that certain classes of diagrams parametrize the same positroid cells. On the other hand, in order to get a parametrization of the associated positroid cell from the plabic graphs, one must assign weights to the vertices and used them to compute Pl\"{u}cker coordinates \cite[Section 11]{Postnikov}, while the Wilson loop diagrams \emph{are} a parametrization of the associated positroid. That is, one can compute the Pl\"{u}cker coordinates directly from the associated matrices.  \sanote{This para is in answer to 1 and 4 of report Y. Should it be moved (in a modified form) to the begining of section 3? Should it be in both places?}

@@

\begin{dfn} \label{VPropdfn}
Let $W = (\cP, V)$ be a Wilson loop diagram.
\begin{enumerate}
\item For $p = (i,j) \in \cP$, let $V(p) = \{i, i+1, j, j+1\}$ denote the set of {\bf vertices supporting} $p$. For a set of propagators $P \subseteq \cP$, define 
\[V(P) = \bigcup_{p \in P} V(p)\]
to be the {\bf vertex support} of $P$.
\item For $U \subseteq V$, the set of {\bf propagators supported on $U$} is denoted by
\[\Prop(U) = \{ p \in \cP\ |\ V(p) \cap U \neq \emptyset \}.\]
Note that a propagator in $\Prop(U)$ may not have its entire support contained in $U$. 
\item Vertices of $W$ that do not support any propagators are called {\bf non-supporting}.
\end{enumerate}
\end{dfn}

@@

\begin{dfn}\label{admisdfn}
A Wilson loop diagram $W = (\cP, V)$ is called {\bf admissible} if the following conditions hold:
\begin{enumerate}
\item $|V| \geq |\cP| + 4$.
\item For each non-empty subset of propagators, $Q \subseteq \cP$, we have $|V(Q)|\geq |Q| + 3$.
\item There are no crossing propagators: that is, there does not exist ${\{(i,j),(k,l)\} \subseteq \cP}$ such that $i < k < j < l$.
\end{enumerate}
 \end{dfn}

@@

Note that a subdiagram $(Q,U)$ of an admissible Wilson loop diagram need not be admissible itself: it inherits conditions 2 and 3 automatically, but we could have $|U| = |Q| + 3$. If a Wilson loop diagram satisfies conditions 2 and 3 of Definition~\ref{admisdfn}, we call it {\bf weakly admissible}.

@@

With this motivation in mind, in Section~\ref{sec poles} of this paper we study the denominator $R(W)$ of $\Omega(W)$. The definition of $R(W)$ is as follows.

@@

For our purposes, a {\bf positroid} is\footnote{Note that matroid isomorphism allows arbitrary permutations of the ground set but positroid isomorphism allows only cyclic permutations, so the property of being a positroid is not in general preserved by matroid isomorphism.} a matroid $M$ (with ground set $[n]$ and bases set $\cB \subseteq \binom{[n]}{k}$) which can be represented by an element of the positive Grassmannian $\Gr(k,n)$. In other words, there exists a full-rank $k\times n$ real matrix whose $k\times k$ minors are all nonnegative and such that the minor comprised of the columns indicated by the set $J$ 
is positive if and only if $J \in \cB$.

@@

\begin{dfn}\label{def:grassmann necklace}
A {\bf Grassmann necklace} of type $(k,n)$ is a sequence $(I_1, \dots, I_n)$ of $n$ sets $I_i \in \binom{[n]}{k}$ such that for each $i \in [n]$ the following statements are true:
\begin{itemize}
\item if $i \in I_i$, then $I_{i+1} = \big(I_i \backslash \{i\}\big) \cup \{j\}$ for some $j \in[n]$.
\item if $i \not\in I_i$, then $I_{i+1} = I_i$.
\end{itemize}
By convention, we set $I_{n+1} = I_1$.
\end{dfn}

@@

The rows and columns of a Le diagram are labelled as follow: given a Le diagram fitting inside a $k\times (n-k)$ box, arrange the numbers $1,2, \dots, n$ along its southeast border, starting from the top-right corner. See Figure \ref{fig:row column numbering} for examples.

@@

An algorithm for constructing the Le diagram associated to a Grassmann necklace was given by Agarwala and Fryer in \cite{reversingOh}. Since we will make use of this algorithm in Section~\ref{sec dim} below, we summarize the process here.
\begin{algorithm}\label{alg:GN to Le} \ \cite[Algorithm 2]{reversingOh}
Let $(I_1,\dots,I_n)$ be a Grassmann necklace of type $(k,n)$. Within a $k \times(n-k)$ square, draw the Young diagram whose rows are labelled by $I_1$ (as per the convention above).

For each $i$, $2 \leq i \leq n$ perform the following steps:
\begin{itemize}
\item Write \[I_1 \setminus I_i = \{a_1 > a_2 > \dots > a_r\}, \quad I_i \setminus I_1 = \{b_1 < b_2 < \dots < b_r\},\]
where the inequalities denote the $<_1$ order (subscripts suppressed for clarity).
\item For $1 \leq j \leq r$ , place a $+$ in square $(a_j,b_j)$ of the diagram. (We will refer to this $+$ as being {\em in the $a_j \rightarrow b_j$ position}.)
\end{itemize}
After performing the above for $2 \leq i \leq n$, place a $0$ in any remaining unfilled boxes.
\end{algorithm}

@@

In \cite{wilsonloop}, Agarwala and Marin-Amat show that $M(W)$ can also be read directly from the Wilson loop diagram itself:

@@

  Because the nonzero entries of $C(W)$ are independent indeterminants, $J$ is an independent set if and only if there is some choice of $|J|$ nonzero entries of $C(W)$ one in each row associated to an element of $J$ and each in different columns. Each entry in $C(W)$ identifies a propagator by the row of the entry and a vertex by the column of the entry.  The entry is nonzero if and only if the propagator is supported on that vertex.  \hlfix{Consequently, take a choice of $|J|$ nonzero entries of $C(W)$, one in each row associated to an element of $J$ and each in different columns;  each such choice is equivalent to an assignment of the propagators of $J$ to supporting vertices so that no two are assigned to the same vertex.}{Added parenthetical commas according to M.23. better?  I did a bit more, we can discuss}  Such an assignment of the propagators of $J$ to supporting vertices is exactly a map $f$ as described in the statement, hence proving the result.
\end{proof}

@@

@@

\begin{rmk}\label{rem:props of length 2 and 3} 
  The following observations about configurations of propagators of short length in a weakly admissibly Wilson loop diagram $W$ are easily verified:
  \vspace{-0.5em}
 \begin{enumerate}
\item If $p = (i,i+3)$ is a propagator of length 3, then the middle vertex $i+2$ supports at most one propagator.\item If every vertex in $W$ supports at least one propagator, then $W$ admits at least one propagator of length 2.  By the same reasoning, if $p=(i,j)$ is a propagator of $W$ and every vertex in the interval $[i,j]$ supports at least one propagator, then there is at least one propagator of length $2$ in $\mathcal{P}_{in}(p, <_i)$.
\end{enumerate}
\end{rmk}

@@

\begin{lem}\label{lem sian}
  Let $W$ be a weakly admissible Wilson loop diagram with at least 5 vertices and in which each vertex supports at least one propagator.  Then at least one of the following two conditions holds:
  \vspace{-0.5em}
  \begin{enumerate}
    \item $W$ has a propagator of length at most 6 with a propagator of length 2 on one side of it and nothing else on that side.\label{item big and 2} \todo{M.28 may need to be propagated}
    \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator has an end between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
  \end{enumerate}
See Figure~\ref{fig: small configs} for an illustration of the two configurations.
\end{lem}

@@

We will inductively construct sequences of propagators $\{p_r\}$ and $\{q_r\}$, with $\ell(p_r) = 2$ for each $r$ and such that either of the following are true:
\begin{itemize}
\item $p_r$ forms part of configuration \ref{item big and 2} or \ref{item pair of 2s} from the statement, at which point the induction terminates, 
  %a configuration \eqref{eq:2 prop config} in $D$
{\em or} 
\item there is a propagator $q_r$ satisfying $\ell(q_r) \geq 4$, and $\{p_1, \ldots, p_r, q_1, \ldots, q_{r-1}\}$ are all on the same side of $q_r$.  
\end{itemize}

@@

From our existing assumptions, we know the following facts: $p_1$ is not in configuration \ref{item pair of 2s}, there are no propagators of length $3$, and every vertex supports at least one propagator.  Therefore, there must be a propagator of length $\geq 4$ with one end on edge $j_1$ or on edge $j_1-1$ or on edge $j_1-2$.  Let $q_1 = (i_1, k_1)$ be this propagator, oriented such that $p_1 \in \cP_{out}(q_1,<_{i_1})$; see Figure~\ref{fig base case lem sian}. This completes the base case.

@@

Let $W_r := (\cP_{in}(q_r),[n])$ be the subdiagram of $W$ consisting only of those propagators inside $q_r$ (including $q_r$ itself); in particular $W_r$ contains none of the previous $p_i$ or $q_i$. By the original hypotheses on $W$, every vertex in $[i_r,k_{r+1}]$ (of which there are at least 4, since $\ell(q_r) \geq 4$) must support at least one propagator. Therefore, $W_r$ admits at least one propagator of length 2 (by Remark~\ref{rem:props of length 2 and 3}) and no propagators of length $3$ (by our assumption on $W$).

@@

The first case is that $i_r \leq j_{r+1} \leq i_r+2$ and $k_r-2 \leq j_{r+1}+2 \leq k_{r}$ (so $p_{r+1}$ has one end before $i_{r} + 3$ and the other after $k_{r} - 2$, i.e. there are at most two vertices between an endpoint of $p_{r+1}$ and an endpoint of $q_r$).  Since $p_{r+1}$ has length 2, it must be that $(i_r+3)+1 \geq k_r-2$ and so $q_r$ has length $\leq 6$.  By the minimality assumption on $q_r$, no propagator in $W_r$ has $q_r$ on one side and $p_{r+1}$ on the other side. Therefore, any propagator in $W_r$ other than $q_r$ and $p_{r+1}$ must be of the form $(i,j)$ with $i_r\leq i < j\leq i_r+2$ or $k_r-2 \leq i < j\leq k_r$. Both of these require that $(i,j)$ has length 2, and so we have configuration \ref{item pair of 2s} which we have already assumed does not occur.  Consequently, $W_r$ contains only the two propagators $q_r$ and $p_{r+1}$, yielding configuration \ref{item big and 2} from the lemma statement and again contradicting our assumption. Therefore, this first case cannot occur.

@@

\begin{algorithm}\label{alg:put GN on WLD}
Let $W = (\cP, [n])$ be an admissible Wilson loop diagram. In order to construct the set $I_i^W$ for $i \in [n]$, perform the following steps:

\begin{enumerate}
\item Fix a vertex $i \in [n]$, the {\bf starting vertex}. Set $j:=i$ and $I_i^W = \emptyset$.
\item While $\cP \neq \emptyset$, perform the following steps:
\begin{enumerate}
\item {\em Step $j$ for starting vertex $i$}: If $\Prop(j) = \emptyset$, do nothing. Else, let $p \in \Prop(j)$ be the clockwise-most propagator supported on $j$. Write $I_i^W = I_i^W\cup \{j\}$, and delete propagator $p$ from the diagram.
\item Increment $j$ by 1 and repeat from (a).
\end{enumerate}
\end{enumerate}
\end{algorithm}

@@

Since $I_i(p) \neq b$, there must exist a propagator $q$ inside of $(p,<_i)$ with $I_i(q) = b$. The propagator $q$ cannot end on the edge $b-1$, as this would contradict the minimality of $p$, so we have $q = (d,b)$ with $a <_i d <_i b$, and $I_i(q) = b$.

In order for $q$ to remain unassigned until the algorithm reaches vertex $b$, there must be another propagator $r$ with an end on edge $d$ and $I_i(r) = d+1$; the only way this can occur is if $r$ is outside of $(q,<_i)$ but inside $(p,<_i)$. But now $r$ contributes its fourth vertex to $I_i$, again contradicting the minimality of $p$.
\end{proof}

@@

In each of the four cases, when we remove the propagator labelled $p$ we obtain a diagram which satisfies the statement of the theorem by the induction hypothesis, and contains a propagator ${q = (i,j)}$ with no other propagators inside it (with respect to the $<_i$ orientation). Note that this region may or may not contain non-supporting vertices, which we will call $l, l+1, \ldots$ as necessary. Let $V$ be the diagram obtained by removing the propagator $p$ from $W$ (Figure \ref{fig V diagram}). The diagram $V$ is guaranteed to be an admissible diagram, since it was formed by removing a propagator from a diagram that was at least weakly admissible. \todo{Make certain we don't start sentences with simbols}

@@

We first calculate $I^{W}_w$ for a starting vertex ${w \in [n]\backslash \{l, l+1, \ldots,j,j+1\}}$. Note that $p$ has no effect on other propagators for starting vertices in this range (since $p$ will be the final propagator encountered by the algorithm) so if $r \neq p$, then $I_w^W(r) = I_w^V(r)$. Meanwhile, the value of $I^{W}_w(p)$ depends on which step in the algorithm the propagator $q$ contributes a vertex in the diagram $V$, i.e. on the value of $I^{V}_w(q)$. Thus, if $w\in J_q^{V}(i)$ then 
    \[
    I_w^{W}(r) =  \begin{cases}
        \max\{i+1, m\} & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p
      \end{cases} 
    \]
    while if $w\in J_q^{V}(i+1)$ or $w\in J_q^{V}(j)$ then
    \[
    I_w^{W}(r) =  \begin{cases}
        l & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p \;.
      \end{cases} 
      \]
We also need to understand $I^{W}_w$ for $w \in \{l,l+1,\ldots,j,j+1\}$. For the majority 
%$w \in [l, l+a-1]$} 
%I left this as a comment so we can add it in if necessary, but I don't think we need this level of precision in this sentence: we're just signposting what we're going to do in detail shortly.
of these vertices, we use the following observation: if $p$ is the first propagator to be assigned a value by $I_w^{W}$, then the remainder of $I_w^{W}$ proceeds identically to the assignments of $I^{V}_{w+1}$ (recall Remark~\ref{rmk algorithm locally same}).  Thus we have for any $0\leq b <a$
    \[
    I_{l+b}^{W}(r) = \begin{cases}
      l+b & \text{if } r=p\\
      I_{l+b+1}^{V}(r) & \text{if } r\neq p
    \end{cases}
    \]
Similarly, if $j$ is in the support of $p$, then we have
     \[
       I_j^{W}(r) = \begin{cases}
         j & \text{if $r=p$ and $j$ is in the support of $p$}\\
         I_{j+1}^{V}(r) & \text{if $r\neq p$ and $j$ is in the support of $p$} \;.
       \end{cases} 
       \]
If $j$ is not in the support of $p$, then we must be in Case 2 of Figure~\ref{fig 3 cases} with two vertices in the right hand region.  In this case, if we start the algorithm at $j$ we need to know whether there will be any unassigned propagators other than $p$ when we reach vertex $i$, so as to know what $p$ contributes.

@@

Fix $n$, and suppose for a contradiction that there exists an admissible diagram for which there exists an $i$ with $m\in I_i\setminus \{i\}$ and $m \not\in I_{i+1}$.  Let $W$ be such a counterexample with the minimal number of propagators.

@@

Now let $W' = (\cP_{out}(p,<_i), [n])$, i.e. the diagram obtained from $W$ by removing both $p$ and all propagators inside of $p$. The diagram $W'$ has strictly fewer propagators than $W$ did.

@@

Let $W'$ be the diagram obtained from $W$ by removing only the propagator $p$.  We have
\begin{align*}
  I_i^{W} \backslash \{i\} & = I_{i+1}^{W'} \\
  I_{i+1}^{W} \backslash \{i+1\} & = I_{i+2}^{W'}
\end{align*}
since in both cases the algorithm in $W'$ proceeds identically to that in $W$ after assigning $p$. Since $m \neq i+1$, we have $m\in I_{i+1}^{W'}\setminus\{i+1\}$ but $m\not\in I_{i+2}^{W'}$, contradicting the minimality of $W$. This completes the proof.
\end{proof}

>>>>

This paper is the second in a two part series investigating the combinatorics and geometry underlying Wilson loop diagrams in SYM $N=4$ theory. This series lays out several results about the relationship between Wilson loop diagrams and the positroid cells that give a CW complex structure to the positive Grassmannian. This paper is concerned with identifying which positroid cells correspond to which Wilson loop diagrams, and how this translates to a geometric tiling of a subspace of the positive Grassmannians.

@@

It is worth noting at this point that the \hlfix{combinatorics of the Wilson loop diagrams are different from the combinatorics of the Amplituhedron}{I think we should discuss this paragraph -- it may be misleading in a bad way}, just as the the volume forms associated to the BCFW diagrams are different from those associated to the Wilson Loop diagrams. For instance, the BCFW are most readily related to the geometry of a postive Grassmannian via plabic graphs. Meanwhile, the Wilson loop diagrams correspond to matrices with variable valued entries (see section \ref{section WLD background}) and Grassmann Necklaces (see Algorithm \ref{alg:put GN on WLD}).  These two combinatorial representations of the positive Grassmannians have different strengths and weaknesses, and it is not possible to give a one to one translation of the combinatorial tools used for the Amplituhedron and BCFW diagrams, and the combinatorial tools used for the Wilson loop diagrams, associated matrices and Grassmann Necklaces. For instance, square moves and merge-expand moves give different graphical representations of the same positroid cell. There is no equivalent diagramatical equivalence for Wilson loop diagrams, though it has been shown (see \cite{wilsonloop, generalcombinatoricsI}) that certain classes of diagrams parametrize the same positroid cells. On the other hand, in order to get a parametrization of the associated positroid cell from the plabic graphs, one must assign weights to the vertices and used them to compute Pl\"{u}cker coordinates \cite[Section 11]{Postnikov}, while the Wilson loop diagrams \emph{are} a parametrization of the associated positroid. That is, one can compute the Pl\"{u}cker coordinates directly from the associated matrices.  \sanote{This para is in answer to 1 and 4 of report Y. Should it be moved (in a modified form) to the begining of section 3? Should it be in both places?}

@@

\begin{dfn} \label{VPropdfn}
Let $W = (\cP, V)$ be a Wilson loop diagram.
\begin{enumerate}
\item For $p = (i,j) \in \cP$, let $V(p) = \{i, i+1, j, j+1\}$ denote the set of {\bf vertices supporting} $p$. For a set of propagators $P \subseteq \cP$, define 
\[V(P) = \bigcup_{p \in P} V(p)\]
to be the {\bf vertex support} of $P$.
\item For $U \subseteq V$, the set of {\bf propagators supported on $U$} is denoted by
\[\Prop(U) = \{ p \in \cP\ |\ V(p) \cap U \neq \emptyset \}.\]
Note that a propagator in $\Prop(U)$ does not necessarily have its entire support contained in $U$. 
\item Vertices of $W$ that do not support any propagators are called {\bf non-supporting}.
\end{enumerate}
\end{dfn}

@@

\begin{dfn}\label{admisdfn}
A Wilson loop diagram $W = (\cP, V)$ is called {\bf admissible} if the following conditions hold.
\begin{enumerate}
\item $|V| \geq |\cP| + 4$.
\item For each non-empty subset of propagators, $Q \subseteq \cP$, we have $|V(Q)|\geq |Q| + 3$.
\item There are no crossing propagators. That is, there does not exist ${\{(i,j),(k,l)\} \subseteq \cP}$ such that $i < k < j < l$.
\end{enumerate}
 \end{dfn}

@@

Note that a subdiagram $(Q,U)$ of an admissible Wilson loop diagram need not be admissible itself.  It inherits conditions 2 and 3 automatically, but we could have $|U| = |Q| + 3$. If a Wilson loop diagram satisfies conditions 2 and 3 of Definition~\ref{admisdfn}, we call it {\bf weakly admissible}.

@@

With this motivation in mind, in Section~\ref{sec poles} of this paper we study the denominator $R(W)$ of $\Omega(W)$. The definition of $R(W)$ is as follows:

@@

For our purposes, a {\bf positroid} is\footnote{Note that matroid isomorphism allows arbitrary permutations of the ground set but positroid isomorphism allows only cyclic permutations, so the property of being a positroid is not in general preserved by matroid isomorphism.} a matroid $M$ (with ground set $[n]$ and set of bases $\cB \subseteq \binom{[n]}{k}$) which can be represented by an element of the positive Grassmannian $\Gr(k,n)$. In other words, there exists a full-rank $k\times n$ real matrix whose $k\times k$ minors are all nonnegative and such that the minor comprised of the columns indexed by elements of $J$ 
is positive if and only if $J \in \cB$.

@@

\begin{dfn}\label{def:grassmann necklace}
A {\bf Grassmann necklace} of type $(k,n)$ is a sequence $(I_1, \dots, I_n)$ of $n$ sets $I_i \in \binom{[n]}{k}$ such that for each $i \in [n]$ the following statements are true.
\begin{itemize}
\item If $i \in I_i$, then $I_{i+1} = \big(I_i \backslash \{i\}\big) \cup \{j\}$ for some $j \in[n]$.
\item If $i \not\in I_i$, then $I_{i+1} = I_i$.
\end{itemize}
By convention, we set $I_{n+1} = I_1$.
\end{dfn}

@@

The rows and columns of a Le diagram are labelled as follows:  given a Le diagram fitting inside a $k\times (n-k)$ box, arrange the numbers $1,2, \dots, n$ along its southeast border, starting from the top-right corner. See Figure \ref{fig:row column numbering} for examples.

@@

An algorithm for constructing the Le diagram associated to a Grassmann necklace was given by Agarwala and Fryer in \cite{reversingOh}. Since we will make use of this algorithm in Section~\ref{sec dim}, we summarize the process here.
\begin{algorithm}\label{alg:GN to Le} \ \cite[Algorithm 2]{reversingOh}
Let $(I_1,\dots,I_n)$ be a Grassmann necklace of type $(k,n)$. Within a $k \times(n-k)$ square, draw the Young diagram whose rows are labelled by $I_1$ (as per the convention above).

For each $i$, $2 \leq i \leq n$ perform the following steps.
\begin{itemize}
\item Write \[I_1 \setminus I_i = \{a_1 > a_2 > \dots > a_r\}, \quad I_i \setminus I_1 = \{b_1 < b_2 < \dots < b_r\},\]
where the inequalities denote the $<_1$ order (subscripts suppressed for clarity).
\item For $1 \leq j \leq r$ , place a $+$ in square $(a_j,b_j)$ of the diagram. (We will refer to this $+$ as being {\em in the $a_j \rightarrow b_j$ position}.)
\end{itemize}
After performing the above for $2 \leq i \leq n$, place a $0$ in any remaining unfilled boxes.
\end{algorithm}

@@

In \cite{wilsonloop}, Agarwala and Marin-Amat show that $M(W)$ can also be read directly from the Wilson loop diagram itself.

@@

  Because the nonzero entries of $C(W)$ are independent indeterminants, $J$ is an independent set if and only if there is some choice of $|J|$ nonzero entries of $C(W)$ one in each row associated to an element of $J$ and each in different columns. Each entry in $C(W)$ identifies a propagator by the row of the entry and a vertex by the column of the entry.  The entry is nonzero if and only if the propagator is supported on that vertex.  \hlfix{Consequently, take a choice of $|J|$ nonzero entries of $C(W)$, one in each row associated to an element of $J$ and each in different columns.  Each such choice is equivalent to an assignment of the propagators of $J$ to supporting vertices so that no two are assigned to the same vertex.}{Added parenthetical commas according to M.23. better?  I did a bit more, we can discuss}  Such an assignment of the propagators of $J$ to supporting vertices is exactly a map $f$ as described in the statement, hence proving the result.
\end{proof}

@@

The flavour of the calculations is similar to \cite{CGdyck}\footnote{Thanks to a referee for pointing this paper out.} as in both cases the bijections are very explicit with a similar iterative flavour using Le diagrams and Grassmann necklaces related to another class of objects, for us Wilson loop diagrams and for them unit interval orders.  For them, as us, the Le diagrams are particularly useful for understanding the dimensions of positroid cells since the dimension becomes the count of the number of plusses.  The ubiquitous Catalan numbers arise for them, as for us in \cite{generalcombinatoricsI}.  The specific subclasses of positroids we work with are, however, different.  This basic methodology of gaining insight from bijections is very common in combinatorics.

@@

\begin{rmk}\label{rem:props of length 2 and 3} 
  The following observations about configurations of propagators of short length in a weakly admissibly Wilson loop diagram $W$ are easily verified.
  \vspace{-0.5em}
 \begin{enumerate}
\item If $p = (i,i+3)$ is a propagator of length 3, then the middle vertex $i+2$ supports at most one propagator.\item If every vertex in $W$ supports at least one propagator, then $W$ admits at least one propagator of length 2.  By the same reasoning, if $p=(i,j)$ is a propagator of $W$ and every vertex in the interval $[i,j]$ supports at least one propagator, then there is at least one propagator of length $2$ in $\mathcal{P}_{in}(p, <_i)$.
\end{enumerate}
\end{rmk}

@@

\begin{lem}\label{lem sian}
  Let $W$ be a weakly admissible Wilson loop diagram with at least 5 vertices and in which each vertex supports at least one propagator.  Then at least one of the following two conditions holds.
  \vspace{-0.5em}
  \begin{enumerate}
    \item $W$ has a propagator of length at most 6 with a propagator of length 2 on one side of it and nothing else on that side.\label{item big and 2} \todo{M.28 may need to be propagated}
    \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator has an end between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
  \end{enumerate}
See Figure~\ref{fig: small configs} for an illustration of the two configurations.
\end{lem}

@@

We will inductively construct sequences of propagators $(p_r)$ and $(q_r)$, with $\ell(p_r) = 2$ for each $r$ and such that either of the following are true:
\begin{itemize}
\item the propagator $p_r$ forms part of configuration \ref{item big and 2} or \ref{item pair of 2s} from the statement, at which point the induction terminates, 
  %a configuration \eqref{eq:2 prop config} in $D$
{\em or} 
\item there is a propagator $q_r$ satisfying $\ell(q_r) \geq 4$, and $\{p_1, \ldots, p_r, q_1, \ldots, q_{r-1}\}$ are all on the same side of $q_r$.  
\end{itemize}

@@

From our existing assumptions, we know the following facts: $p_1$ is not in configuration \ref{item pair of 2s}, there are no propagators of length $3$, and every vertex supports at least one propagator.  Therefore, there must be a propagator of length at least 4 with one end on edge $j_1$ or on edge $j_1-1$ or on edge $j_1-2$.  Let $q_1 = (i_1, k_1)$ be this propagator, oriented such that $p_1 \in \cP_{out}(q_1,<_{i_1})$; see Figure~\ref{fig base case lem sian}. This completes the base case.

@@

Let $W_r := (\cP_{in}(q_r),[n])$ be the subdiagram of $W$ consisting of those propagators inside $q_r$ (including $q_r$ itself); in particular $W_r$ contains none of the previous $p_i$ or $q_i$. By the original hypotheses on $W$, every vertex in $[i_r,k_{r+1}]$ (of which there are at least 4, since $\ell(q_r) \geq 4$) must support at least one propagator. Therefore, $W_r$ admits at least one propagator of length 2 (by Remark~\ref{rem:props of length 2 and 3}) and no propagators of length $3$ (by our assumption on $W$).

@@

The first case is that $i_r \leq j_{r+1} \leq i_r+2$ and $k_r-2 \leq j_{r+1}+2 \leq k_{r}$ (so $p_{r+1}$ has one end before $i_{r} + 3$ and the other after $k_{r} - 2$, i.e. there are at most two vertices between an endpoint of $p_{r+1}$ and an endpoint of $q_r$).  Since $p_{r+1}$ has length 2, it must be that $(i_r+3)+1 \geq k_r-2$ and so $q_r$ has length at most 6.  By the minimality assumption on $q_r$, no propagator in $W_r$ has $q_r$ on one side and $p_{r+1}$ on the other side. Therefore, any propagator in $W_r$ other than $q_r$ and $p_{r+1}$ must be of the form $(i,j)$ with $i_r\leq i < j\leq i_r+2$ or $k_r-2 \leq i < j\leq k_r$. Both of these require that $(i,j)$ has length 2, and so we have configuration \ref{item pair of 2s} which we have already assumed does not occur.  Consequently, $W_r$ contains only the two propagators $q_r$ and $p_{r+1}$, yielding configuration \ref{item big and 2} from the lemma statement and again contradicting our assumption. Therefore, this first case cannot occur.

@@

\begin{algorithm}\label{alg:put GN on WLD}
Let $W = (\cP, [n])$ be an admissible Wilson loop diagram. In order to construct the set $I_i^W$ for $i \in [n]$, perform the following steps.

\begin{enumerate}
\item Fix a vertex $i \in [n]$, the {\bf starting vertex}. Set $j:=i$ and $I_i^W = \emptyset$.
\item While $\cP \neq \emptyset$, perform the following steps.
\begin{enumerate}
\item {\em Step $j$ for starting vertex $i$}: If $\Prop(j) = \emptyset$, do nothing. Else, let $p \in \Prop(j)$ be the clockwise-most propagator supported on $j$. Write $I_i^W = I_i^W\cup \{j\}$, and delete propagator $p$ from the diagram.
\item Increment $j$ by 1 and repeat from (a).
\end{enumerate}
\end{enumerate}
\end{algorithm}

@@

Since $I_i(p) \neq b$, there must exist a propagator $q$ inside $(p,<_i)$ with $I_i(q) = b$. The propagator $q$ cannot end on the edge $b-1$, as this would contradict the minimality of $p$, so we have $q = (d,b)$ with $a <_i d <_i b$, and $I_i(q) = b$.

In order for $q$ to remain unassigned until the algorithm reaches vertex $b$, there must be another propagator $r$ with an end on edge $d$ and $I_i(r) = d+1$; the only way this can occur is if $r$ is outside $(q,<_i)$ but inside $(p,<_i)$. But now $r$ contributes its fourth vertex to $I_i$, again contradicting the minimality of $p$.
\end{proof}

@@

In each of the four cases, when we remove the propagator labelled $p$ we obtain a diagram which satisfies the statement of the theorem by the induction hypothesis, and contains a propagator ${q = (i,j)}$ with no other propagators inside it (with respect to the $<_i$ orientation). Note that this region may or may not contain non-supporting vertices, which we will call $l, l+1, \ldots$ as necessary. Let $V$ be the diagram obtained by removing the propagator $p$ from $W$ (Figure \ref{fig V diagram}). The diagram $V$ is guaranteed to be admissible, since it was formed by removing a propagator from a diagram that was at least weakly admissible. \todo{Make certain we don't start sentences with simbols}

@@

We first calculate $I^{W}_w$ for a starting vertex ${w \in [n]\backslash \{l, l+1, \ldots,j,j+1\}}$. Note that $p$ has no effect on other propagators for starting vertices in this range (since $p$ will be the final propagator encountered by the algorithm) so if $r \neq p$, then $I_w^W(r) = I_w^V(r)$. Meanwhile, the value of $I^{W}_w(p)$ depends on which step in the algorithm the propagator $q$ contributes a vertex in the diagram $V$, i.e. on the value of $I^{V}_w(q)$. Thus, if $w\in J_q^{V}(i)$ then 
    \[
    I_w^{W}(r) =  \begin{cases}
        \max\{i+1, m\} & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p
      \end{cases} 
    \]
    while if $w\in J_q^{V}(i+1)$ or $w\in J_q^{V}(j)$ then
    \[
    I_w^{W}(r) =  \begin{cases}
        l & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p \;.
      \end{cases} 
      \]
We also need to understand $I^{W}_w$ for $w \in \{l,l+1,\ldots,j,j+1\}$. For the majority 
%$w \in [l, l+a-1]$} 
%I left this as a comment so we can add it in if necessary, but I don't think we need this level of precision in this sentence: we're just signposting what we're going to do in detail shortly.
of these vertices, we use the following observation: if $p$ is the first propagator to be assigned a value by $I_w^{W}$, then the remainder of $I_w^{W}$ proceeds identically to the assignments of $I^{V}_{w+1}$ (recall Remark~\ref{rmk algorithm locally same}).  Thus we have for any $0\leq b <a$
    \[
    I_{l+b}^{W}(r) = \begin{cases}
      l+b & \text{if } r=p\\
      I_{l+b+1}^{V}(r) & \text{if } r\neq p\;.
    \end{cases}
    \]
Similarly, if $j$ is in the support of $p$, then we have
     \[
       I_j^{W}(r) = \begin{cases}
         j & \text{if $r=p$ and $j$ is in the support of $p$}\\
         I_{j+1}^{V}(r) & \text{if $r\neq p$ and $j$ is in the support of $p$} \;.
       \end{cases} 
       \]
If $j$ is not in the support of $p$, then we must be in Case 2 of Figure~\ref{fig 3 cases} with two vertices in the right hand region.  In this case, if we start the algorithm at $j$ we need to know whether there will be any unassigned propagators other than $p$ when we reach vertex $i$, so as to know what $p$ contributes.

@@

Fix $n$, and suppose, by way of contradiction that there exists an admissible diagram for which there exists an $i$ with $m\in I_i\setminus \{i\}$ and $m \not\in I_{i+1}$.  Let $W$ be such a counterexample with the minimal number of propagators.

@@

Now let $W' = (\cP_{out}(p,<_i), [n])$, i.e. the diagram obtained from $W$ by removing both $p$ and all propagators inside $p$. The diagram $W'$ has strictly fewer propagators than $W$ did.

@@

Let $W'$ be the diagram obtained from $W$ by removing the propagator $p$.  We have
\begin{align*}
  I_i^{W} \backslash \{i\} & = I_{i+1}^{W'} \\
  I_{i+1}^{W} \backslash \{i+1\} & = I_{i+2}^{W'}
\end{align*}
since in both cases the algorithm in $W'$ proceeds identically to that in $W$ after assigning $p$. Since $m \neq i+1$, we have $m\in I_{i+1}^{W'}\setminus\{i+1\}$ but $m\not\in I_{i+2}^{W'}$, contradicting the minimality of $W$. This completes the proof.
\end{proof}
